### 2021-04-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

\IncMargin{1em}
\begin{algorithm}[h]\small
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
    \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
    Insert $c_{\addr{1}}$ to $G$ as a new entry \;
    \For{$i\leftarrow 2$ \KwTo $n$}
    {
        $S_{c_{\addr{i}}}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
        \For{$g_{i} \in G$}
        {
            $S_{g_j}$ $\leftarrow$ $\pi(g_{j})$ \;
            $S$ $\leftarrow$ $S_{c_{\addr{i}}} \cap S_{g_j}$  \;
            \If{$S \neq \emptyset$}
            {
                $g_{j} \leftarrow g_{i} \land g_{\addr{i}}$ \;
                \textbf{continue} \;
            }
            Insert $c_{\addr{i}}$ to $G$ as a new entry \;
        }
    }
    \caption{The Maximum Independent Partition}
    \label{algo:max-inde}
\end{algorithm}
\DecMargin{1em}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\textwidth]{./figures/chapter4/workflow.pdf}
    \caption{The workflow of \tool{}.}
    \label{fig:workflow}
\end{figure}

@@

\begin{table}[h!]
    \centering
    %    \resizebox{.8\columnwidth}{!}{
    \caption{\tool{}' main components and sizes}\label{tbl:implementation}
    \begin{tabular}{lr@{~}@{}l}
        \hline
        Component            & \multicolumn{2}{c}{Lines of Code (LOC)}             \\ \hline
        Trace Logging        & 501 lines                               & of C++    \\
        Symbolic Execution   & 14,963 lines                            & of C++    \\
        Data Flow            & 451 lines                               & of C++    \\
        Monte Carlo Sampling & 603 lines                               & of C++    \\
        Others               & 211 lines                               & of Python \\ \hline
        Total                & 16,729 lines                            &           \\\hline
    \end{tabular}
    %    }
\end{table}

@@

\subsection{Benchmarks}\label{sec:eval_countermeasures}
\subsubsection{Bit-slicing}
Bit-slicing is an efficient method to construct constant-time implementation for side channel to mitigation. The basic concept is to implement a function in terms of single-bit logical gate operations, such as AND, XOR, OR, and NOT\@.

@@

if (password <= 0b111)      \\Leaks 5 bits of password
    ret = SBOX[password];   \\Leaks 4 bits of password
      \end{lstlisting}
    \caption{SBOX without BitSlicing}
    \label{fig:SBOX_da}
\end{figure}

@@

ret = l << 1 + r;
\end{lstlisting}
\caption{SBOX with BitSlicing}
\label{fig:SBOX_bitslicing}
\end{figure}
We test \tool\ on bit-slicing. We adopt the SBOX
implementations, commonly used in block ciphers such as DES and AES, with and
without bit-slicing, and apply \tool{} to confirm the mitigation. The SBOX implementation with and without bit-slicing are shown in Figure~\ref{fig:SBOX_bitslicing} and Figure~\ref{fig:SBOX_da}, respectively. Considering an SBOX take some bits derived from a password as input and output 2-bit transform result, the plain implementation
has a range check on the password input and a secret-dependent table lookup while bit-slicing does not.

@@

\subsubsection{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Small Entries.}\label{fig:chapter4:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Big Entries.}\label{fig:chapter4:big_lookup}
\end{figure}

@@

\subsubsection{Password Checker}
\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}
  \end{minipage}
  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter4:pwcheck}
\end{figure}

>>>>

\IncMargin{1em}
\begin{algorithm}[th]\small
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
    \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
    Insert $c_{\addr{1}}$ to $G$ as a new entry \;
    \For{$i\leftarrow 2$ \KwTo $n$}
    {
        $S_{c_{\addr{i}}}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
        \For{$g_{i} \in G$}
        {
            $S_{g_j}$ $\leftarrow$ $\pi(g_{j})$ \;
            $S$ $\leftarrow$ $S_{c_{\addr{i}}} \cap S_{g_j}$  \;
            \If{$S \neq \emptyset$}
            {
                $g_{j} \leftarrow g_{i} \land g_{\addr{i}}$ \;
                \textbf{continue} \;
            }
            Insert $c_{\addr{i}}$ to $G$ as a new entry \;
        }
    }
    \caption{The Maximum Independent Partition}
    \label{algo:max-inde}
\end{algorithm}
\DecMargin{1em}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.85\textwidth]{./figures/chapter4/workflow.pdf}
    \caption{The workflow of \tool{}.}
    \label{fig:workflow}
\end{figure}

@@

\begin{table}[ht]
    \centering
    %    \resizebox{.8\columnwidth}{!}{
    \caption{\tool{}' main components and sizes}\label{tbl:implementation}
    \begin{tabular}{lr@{~}@{}l}
        \hline
        Component            & \multicolumn{2}{c}{Lines of Code (LOC)}             \\ \hline
        Trace Logging        & 501 lines                               & of C++    \\
        Symbolic Execution   & 14,963 lines                            & of C++    \\
        Data Flow            & 451 lines                               & of C++    \\
        Monte Carlo Sampling & 603 lines                               & of C++    \\
        Others               & 211 lines                               & of Python \\ \hline
        Total                & 16,729 lines                            &           \\\hline
    \end{tabular}
    %    }
\end{table}

@@

\subsection{Benchmarks}\label{sec:eval_countermeasures}
\subsubsection*{Bit-slicing}
Bit-slicing is an efficient method to construct constant-time implementation for side channel to mitigation. The basic concept is to implement a function in terms of single-bit logical gate operations, such as AND, XOR, OR, and NOT\@.

@@

if (password <= 0b111)      \\Leaks 5 bits of password
    ret = SBOX[password];   \\Leaks 4 bits of password
      \end{lstlisting}
    \caption{SBOX without bitslicing}
    \label{fig:SBOX_da}
\end{figure}

@@

ret = l << 1 + r;
\end{lstlisting}
\caption{SBOX with bitslicing}
\label{fig:SBOX_bitslicing}
\end{figure}
We test \tool\ on bit-slicing. We adopt the SBOX
implementations, commonly used in block ciphers such as DES and AES, with and
without bit-slicing, and apply \tool{} to confirm the mitigation. The SBOX implementation with and without bit-slicing are shown in Figure~\ref{fig:SBOX_bitslicing} and Figure~\ref{fig:SBOX_da}, respectively. Considering an SBOX take some bits derived from a password as input and output 2-bit transform result, the plain implementation
has a range check on the password input and a secret-dependent table lookup while bit-slicing does not.

@@

\subsubsection*{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup tables with small entries.}\label{fig:chapter4:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup tables with big entries.}\label{fig:chapter4:big_lookup}
\end{figure}

@@

\subsubsection*{Password Checker}
\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}
  \end{minipage}
  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter4:pwcheck}
\end{figure}
